Influence of Connectivity on Dung Beetle Communities

### 2025-05-31 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
tweaks and starts to results

 - We also dried and weighed individuals to estimate biomass  
 - what guides/keys did you do to ID?  
 - "Voucher specimens of species I collected will be deposited at the Florida State Collection of Arthropods" (https://thefsca.org/services/specimen-donations/)

## Analyses

@@

>>>>

@@

## Community Composition and Abundance

Overall, 5213 total dung beetles were collected belonging to 16 species. The most dominant species were _Canthon vigilans_ (n = 1300) , _Ateuchus lecontei_ (n = 1112), and _Phanaeus igneus_ ( n =  958) (Table 1). All but four species were found in every patch type. _Onthophagus concinnus_ was found in the matrix and winged patches, while _Onthophagus striatulus_ was found in matrix habitat and rectangular patches. _Geotrupes blackburnii_ and _Onthophagus tuberculifrons_ were the only species restricted to one patch type (winged and matrix, respectively).
